---
title: "Kickout"
output:
  flexdashboard::flex_dashboard:
    navbar:
      - title: "Me"
        href: https://mltwelve.com/
        icon: "fa-home"
    theme: yeti
runtime: shiny
---


# Welcome to Kickout!

```{r setup, include=FALSE}
library(DT)
library(dplyr)
library(flexdashboard)
library(shiny)
library(readr)
library(lubridate)
library(ggplot2)
library(plotly)
library(shinyWidgets)
library(tidyr)


# Source the script that generates the 'events' dataset
events <- read_csv("Dataout/all_events.csv")


# events <-  read_csv("https://raw.githubusercontent.com/KirstinLyon/jump_metrics/refs/heads/main/Dataout/all_events.csv?token=GHSAT0AAAAAAC4QU5H3TALWBYUEP4K2ELQ22ALH6MQ")
# Use the 'events' dataset generated by fetch_data.R
start_data <- events  |> 
  mutate(Year = lubridate::year(Date)) |> 
  select(Year, Date, Event, Discipline, Competition, Competitor, Country, Club, Stage,
         Rank, Total, Mark, Elements, Execution, T, D, H, is_complete)  


compact_data <- start_data 

update_raw_data <- reactive({
  compact_data
})



```

## Column {data-width="400"}

**Kickout - Analysing Trampoline Competition Data**

This app provides insights into individual and synchronized trampoline events, focusing on trampoline gymnasts in Denmark, and specifically Københavns Trampoline Club (KTK). It uses data from SportTech.io and is updated each Monday. 

## Column {data-width="600"}



Trends
================

Column {.sidebar}
--------------------------------------------------------------

```{r}

# Sort competitor names alphabetically
sorted_club <- sort(unique(start_data$Club))

selectInput('Club', 'Club',
            choices = sorted_club,
            selected = "KTK")  # Set default to the first name in the sorted list

selectInput('Competitor', 'Competitor', choices = NULL)
selectInput('Discipline', 'Discipline', choices = NULL, selected = "TRA")
selectInput('is_complete', 'Skills', choices = start_data$is_complete, selected = "Complete")
pickerInput(
  inputId = "Stage",
  label = "Select Stage(s):", 
  choices = unique(start_data$Stage),
  selected = c("Final", "Qualification_2"),
  options = list(
    `actions-box` = TRUE,  # Adds "Select All" buttons
    `selected-text-format` = "count > 2"  # Shows count when >2 selected
  ),
  multiple = TRUE  # Allows multiple selections
)


# Observe changes in Club selection to update other inputs
# Observe changes in Club selection to update Competitor input
observeEvent(input$Club, {
  if (input$Club != "") {  # Only update if a club is selected
    filtered_data <- start_data |> filter(Club == input$Club)
    updateSelectInput(session, 'Competitor', choices = sort(unique(filtered_data$Competitor)))
  } else {
    updateSelectInput(session, 'Competitor', choices = NULL)
  }
})

# Observe changes in Competitor selection to update other inputs
observeEvent(input$Competitor, {
  if (input$Competitor != "") {  # Only update if a competitor is selected
    filtered_data <- start_data |>  filter(Competitor == input$Competitor)
    updateSelectInput(session, 'Discipline', choices = sort(unique(filtered_data$Discipline)), selected = "TRA")
    updateSelectInput(session, 'Stage', choices = sort(filtered_data$Stage), selected = c("Final", "Qualification_2"))
    updateSelectInput(session, 'is_complete', choices = sort(unique(filtered_data$is_complete)))
  } else {
    updateSelectInput(session, 'Discipline', choices = NULL, selected = "TRA")
    updateSelectInput(session, 'Stage', choices = NULL, selected = c("Final", "Qualification_2"))
    updateSelectInput(session, 'is_complete', choices = NULL, selected = "Complete")
  }
})

```


## Column {data-width="400"}



### Execution
```{r}
renderPlot({
 update_raw_data() |> 
    filter(Discipline == input$Discipline,
           Stage %in% input$Stage,
           Competitor == input$Competitor,
           is_complete == input$is_complete)  |>
    ggplot(aes(x = Date, y = Execution, colour = Stage)) +
    geom_line(linewidth = 0.95) +
    geom_point(size = 3) +  # This adds dots for each data point
    scale_color_hue(direction = 1) +
    labs( y = "Execution") +
    theme_minimal() +
    theme(legend.position = "top", legend.justification = "right")+
    expand_limits(y = 0)  # This one line forces y-axis to include 0
})
```

### Difficulty
```{r}
renderPlot({
 update_raw_data() |> 
    filter(Discipline == input$Discipline,
           Stage %in% input$Stage,
           Competitor == input$Competitor,
           is_complete == input$is_complete)  |>
    ggplot(aes(x = Date, y = D, colour = Stage)) +
    geom_line(linewidth = 0.95) +
    geom_point(size = 3) +  # This adds dots for each data point
    scale_color_hue(direction = 1) +
    labs( y = "Difficulty") +
    theme_minimal() +
    theme(legend.position = "top", legend.justification = "right")+
    expand_limits(y = 0)  # This one line forces y-axis to include 0
})
```


### Time of Flight (Seconds)

```{r}
renderPlot({
 update_raw_data() |> 
    filter(Discipline == input$Discipline,
           Stage %in% input$Stage,
           Competitor == input$Competitor,
           is_complete == input$is_complete)  |>
    ggplot(aes(x = Date, y = T, colour = Stage)) +
    geom_line(linewidth = 0.95) +
    geom_point(size = 3) +  # This adds dots for each data point
    scale_color_hue(direction = 1) +
    labs(y = "Time of Flight (S)") +
    theme_minimal() +
    theme(legend.position = "top", legend.justification = "right")+
    expand_limits(y = 0)  # This one line forces y-axis to include 0
})
```
### Horizontal Displacement

```{r}
renderPlot({
 update_raw_data() |> 
    filter(Discipline == input$Discipline,
           Stage %in% input$Stage,
           Competitor == input$Competitor,
           is_complete == input$is_complete)  |>
    ggplot(aes(x = Date, y = H, colour = Stage)) +
    geom_line(linewidth = 0.95) +
    geom_point(size = 3) +  # This adds dots for each data point
    scale_color_hue(direction = 1) +
    labs(y = "Horizontal Displacement") +
    theme_minimal() +
    theme(legend.position = "top", legend.justification = "right")+
    expand_limits(y = 0)  # This one line forces y-axis to include 0
})
```


Column {data-width="600"}
----------------------------------------


### Overall Scores
```{r}

#renderPlot({
#  comp_data <- update_raw_data() |> 
#    filter(Discipline == input$Discipline,
#           Stage %in% input$Stage,
#           Competitor == input$Competitor,
#           is_complete == input$is_complete) |>
#    select(Date, Event, Discipline, Competition, Competitor, Stage,
#           Rank, Total, Mark, Elements, Execution, T, D, H) |> 
#    pivot_longer(cols = c(Execution, T, D, H),
#                 names_to = "Score_Type", 
#                 values_to = "Score")
  
#  ggplot(comp_data,  # You were using 'competition_data' instead of 'comp_data'
#         aes(x = interaction(Competition, Event, sep = " - "), 
#             y = Score, 
#             fill = fct_rev(Score_Type))) +
#    geom_bar(stat = "identity") +
 #   labs(title = "Total Scores by Competition and Event",
#         x = "Competition - Event",
#         y = "Score",
#         fill = "Score Type") +
#    scale_fill_manual(values = c("D" = "#E15759",       # Changed to match your column names
#                                "T" = "#59A14F",
#                                "H" = "#F28E2B",
#                                "Execution" = "#4E79A7")) +
#    theme_minimal() +
#    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
#          plot.title = element_text(hjust = 0.5, face = "bold"),
#          legend.position = "bottom") +
#    guides(fill = guide_legend(reverse = TRUE))
#})


```


Event Overview
================
column {.sidebar}
--------------------------------------------------------------

```{r}

# Set the default selected event in selectInput
selectInput('Event', 'Event', choices = start_data$Event)
selectInput('Competition', 'Competition', choices = NULL)


observeEvent(input$Event, {
  if (input$Event != "") {  # Only update if an event is selected
    filtered_data <- start_data |> filter(Event == input$Event)
    # Update Discipline input, ensuring "TRA" is the default if available
    # Update Competition input
    updateSelectInput(session, 'Competition', choices = sort(unique(filtered_data$Competition)))
  } else {
    # Reset inputs if no event is selected

    updateSelectInput(session, 'Competition', choices = NULL)
  }
})

```

## Column {data-width="400"}

### Execution
```{r}

renderPlot({
 update_raw_data() |> 
        filter(
           Event == input$Event,
           Competition == input$Competition)  |>
ggplot(aes(x = as.numeric(factor(Competitor)), y = Execution)) +
    geom_jitter(width = 0.2, height = 0) +  # Adjust width and height for jitter effect
    theme_minimal() +
    labs(
         x = "Competitor",
         y = "Execution") +
    scale_x_continuous(breaks = NULL)+  # Remove x-axis labels
    expand_limits(y = 0)  # This one line forces y-axis to include 0
})
```

### Time of Flight(Seconds)
```{r}

renderPlot({
 update_raw_data() |> 
        filter(
           Event == input$Event,
           Competition == input$Competition)  |>
ggplot(aes(x = as.numeric(factor(Competitor)), y = T)) +
    geom_jitter(width = 0.2, height = 0) +  # Adjust width and height for jitter effect
    theme_minimal() +
    labs(
         x = "Competitor",
         y = "ToF") +
    scale_x_continuous(breaks = NULL)+  # Remove x-axis labels
    expand_limits(y = 0)  # This one line forces y-axis to include 0
})
```

### Horizontal Displacement
```{r}

renderPlot({
 update_raw_data() |> 
        filter(
           Event == input$Event,
           Competition == input$Competition)  |>
ggplot(aes(x = as.numeric(factor(Competitor)), y = H)) +
    geom_jitter(width = 0.2, height = 0) +  # Adjust width and height for jitter effect
    theme_minimal() +
    labs(
         x = "Competitor",
         y = "HD") +
    scale_x_continuous(breaks = NULL)+  # Remove x-axis labels
    expand_limits(y = 0)  # This one line forces y-axis to include 0
})
```

### Difficulty
```{r}

renderPlot({
 update_raw_data() |> 
        filter(
           Event == input$Event,
           Competition == input$Competition)  |>
ggplot(aes(x = as.numeric(factor(Competitor)), y = D)) +
    geom_jitter(width = 0.2, height = 0) +  # Adjust width and height for jitter effect
    theme_minimal() +
    labs(
         x = "Competitor",
         y = "DD") +
    scale_x_continuous(breaks = NULL)+  # Remove x-axis labels
    expand_limits(y = 0)  # This one line forces y-axis to include 0
})
```

## Column {data-width="600"}

# Data

## Column

### All Events

```{r}
renderDT(
  update_raw_data(), rownames = F, extensions = 'Buttons', filter="top", editable=T,
  options = list(
    dom = 'Blfrtip',
    buttons = c('csv', 'excel', 'pdf', 'print'),
    lengthMenu = list(c(10,50,100,-1),c(10,50,100,"All"))
  )
)
```




